Numerical simulation of two-dimensional heat convection-diffusion with ellipsoid geometries

### 2016-02-01 article/nontech.tex
pushing paper

\begin{abstract}
    This is a test.
\end{abstract}

@@

>>>>

\begin{abstract}
	Ever wonder what's the how to keep your warm bath at the right temperature while helping the environment? This paper introduces and analyzes two-dimensional heat convection-diffusion through the Navier-Stokes formulation of fluid-flow and the classical heat equation. Our mission is to determine the optimal amount of water necessary to maintain the perfect bathtub temperature. BLAH BLAH BLAH
\end{abstract}

@@

The basis of this paper is to develop a model that permits a person to maintain their preferred temperature of the bathtub water while minimizing water consumption.
